\roleheader
    {Amazon Web Services, Inc.}
    {Seattle, Washington}
    {Cloud Support Engineer \RNum{2}}
    {2016-10-01}
    {2018-09-17}

\begin{itemize} \itemsep 0pt
    \item Served as the highest tier of support to mitigate escalations to the respective service team, and improve turn around time on customer issues.
    \item Presented at the ECS Global Subject Matter Expert Summit that had solution architects, product leadership, and premium support.
    \item Point of Contact for ECS / ECR / Fargate / EKS / Docker in support for the service teams, solution architects, and leadership.
    \item The preferred engineer and single point of contact for all things ECS / ECR / Docker for a large customer that successfully launched a feature used by up to 100 million users daily.
    \item Traveled to Berlin to give a presentation on ECS and Prometheus monitoring to a fast growth start-up.
    \item Helped improve process in the support organization by strengthening the relationship with the documentation team to lower customer contacts and clarify complex topics, and led project to create and update internal tooling for premium support
    \item Helped launch Amazon Fargate and Amazon Elastic Kubernetes Service. Work included: Created and delivered training material for premium support on new services, Collaborated with the service team to advocate for customer features, Educated the service team about the premium support experience, and how they can best serve premium support
    \item All job functions of Cloud Support Engineer \RNum{1} continued to be served.
\end{itemize}