\roleheader
    {Amazon Web Services, Inc.}
    {Seattle, Washington}
    {Cloud Support Engineer \RNum{1}}
    {2015-04-13}
    {2016-10-01}

\begin{itemize} \itemsep 0pt
    \item Only AWS premium support Engineer to represent AWS at DockerCon 2016 (Seattle) in 1-on-1 interactions with customers to understand their needs / gather feedback on ECS or AWS.
    \item Provided best practices and conducted troubleshooting for high severity issues for AWS customers who use AWS deployment management services such as (but not limited to): Elastic Beanstalk, EC2 Container Service (ECS), EC2 Container Registry (ECR), CloudFormation, OpsWorks, CodeDeploy, CodePipeline, and CodeCommit.
    \item One of three premium support engineers who met bi-weekly with ECS / ECR product leadership to act as a customer's advocate which included highlighting: feature requests, bug reports, customer complaints, and overall inter-team communication improvements.
    \item Collaborated with AWS premium support of Sydney, Australia office to create introduction, intermediate, advanced, and Subject Matter Expert (SME) level training for ECS, ECR, and Docker.
    \item Inaugural accredited ECS subject matter experts (SME) at Amazon. This accreditation was validated and approved by the creators of Amazon Elastic Container Service. 
    \item Participated in ``Ask an Architect'' at AWS Pop-up Loft in San Francisco, providing 1-on-1, 60 minute sessions to attendees who needed technical deep dives into AWS and Docker, or attendees who expressed interest in learning the fundamentals of cloud computing and DevOps.
    \item Attended the ECS Global Subject Matter Expert Summit and represented the needs of the customers and support to solution architects and product leadership.
\end{itemize}