\setlength\parindent{2em} \textit{
``Jason Swindle is one of the original and founding members of the Cloud Launch Team. He and his teammate are responsible for building a one of the most successful additions to the modern Fanatical Support experience by providing a strategic bridge between sales and support.  This team is credited with increased activations, increased revenue and decreased churn among new customers.  It’s important to note that this team spent the first year onboarding all cloud customers without dedicated systems, broad autonomy and a job description that could change from one day to the next.} \\[5pt]

\setlength\parindent{2em} \textit{
Despite those challenges, Jason Swindle was able to provide his customers with a Fanatical onboarding experience while providing key insights and operational observations to help guide the team’s maturation.  Jason has a real passion for technology that addressed an important gap in the team’s collective skill set. Jason took it upon himself to become an expert on cloud automation. He would later use this skill by designing the infrastructure for the Graffiti project, which earned him the opportunity to speak at last year’s SaltStack Conference. During that time Jason became one of the first people within the industry to become a certified SaltStack Engineer.} \\[5pt]

\setlength\parindent{2em} \textit{
In addition to Jason’s professional skills, he should be recognized for his earnest approach to connecting with those around him. This has translated into Jason building many genuine and lasting professional relationships among his peers and leadership.  As is his way, I know Jason will continue to keep his eye on the horizon of technology and be quick to share with those around him. While Jason’s contributions to the Cloud Launch Team have already had a profound positive influence on Rackspace, I’m eager to see the results of his future endeavors.''}
\rightline{{\rm --- Joseph Palumbo}}  \leavevmode \\[10pt]